---
title: "AssignmentWeek2"
author: "NguyenDuy"
date: "16 November 2016"
output: html_document
---
```{r echo = FALSE}
library(knitr)
opts_chunk$set(cache = TRUE)
```
## Loading and proprocessing the data
Load the data
```{r}
library(dplyr)
library(lubridate)
library(ggplot2)
temporaryFiles <- tempfile()
download.file(url = "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip",temporaryFiles)
activityRaw <- read.csv(unz(temporaryFiles, "activity.csv"))
activity <- activityRaw[!is.na(activityRaw[,1]), ]
unlink(temporaryFiles)
```
Process the data into suitable format
```{r}
tbl_df(activity) %>% group_by(date) -> activity2
```

##Mean total number of steps taken per day
Histogram of total number of steps taken each day
```{r}
activitySum <- summarise(activity2, sum(steps))
hist(activitySum[,2][[1]], main = "Histogram of step each day", xlab = "Number of step")
```

Mean and median of the total number of steps taken per day
```{r}
mean(activitySum[,2][[1]], na.rm = TRUE)
median(activitySum[,2][[1]], na.rm = TRUE)
```

##Average daily activity pattern
```{r}
activity3 <- group_by(activity, interval)
intervalMean <- summarise(activity3, mean(steps, na.rm = TRUE))
plot(intervalMean[,2][[1]], type = "l", main = "Average daily pattern activity", xlab = "5-minute interval", ylab = "Average number of steps")
```

Interval that has maximum number of steps taken 
```{r}
intervalMean[intervalMean[,2] == max(intervalMean[,2]),1][[1]]
```

##Input missing values
Number of missing data
```{r}
dim(activityRaw[which(is.na(activityRaw[,1])), ])[1]
```

Missing data is proxied by average data of interval 
```{r}
activityRaw[which(is.na(activityRaw[,1])), ] %>% 
        mutate(location = which(is.na(activityRaw[,1]))) -> NAData
NAData[,1] <- sapply(NAData[,3], function(x)
        {intervalMean[which(intervalMean[,1][[1]] == x),2][[1]]})
activityProxied <- activityRaw
activityProxied[NAData$location, 1] <- NAData$steps
```

Histogram of total number of steps taken each day for new data set
```{r}
group_by(activityProxied, date) %>% summarise(sum(steps)) -> activityProxiedSum
par(mfrow = c(1,2))
hist(activityProxiedSum[,2][[1]], main = "Histogram of step each day \n(with proxied data)", xlab = "Number of step")
hist(activitySum[,2][[1]], main = "Histogram of step each day\n (without proxied data)", xlab = "Number of step")
```

Mean and median data with proxies
```{r}
mean(activityProxiedSum[,2][[1]])
median(activityProxiedSum[,2][[1]])
```
Mean and median data without proxies
```{r}
mean(activitySum[,2][[1]])
median(activitySum[,2][[1]])
```
The means are not different between proxied and non-proxied data. However, the medians are different.


##Differences in activity patterns between weekdays and weekends
```{r}
activity4 <- mutate(activityProxied, daytype = weekdays(ymd(activityProxied$date)))
activity4[(activity4$daytype == "Sunday"| activity4$daytype == "Saturday"), "daytype"] <- "weekend"
activity4[activity4$daytype != "weekend", "daytype"] <- "weekday"
activity4 <- group_by(activity4, daytype, interval)
daytypeIntMean <- summarise(activity4, mean(steps))
colnames(daytypeIntMean) <- c("daytype", "interval", "averageStep")
qplot(x = interval, y = averageStep, data = daytypeIntMean, 
      facets = daytype~., geom = "line", main = "Average Step during Weekday or Weekend", ylab = "Average Step")
```

##End of analysis

